A meta-analysis of mental rotation ability in the first years of life

### 2022-05-01 code/analysis.Rmd
Create shared table for sensitivity analyses

# Re-run the meta-analysis for different values of r_assumed
seq(-0.9, 0.9, by = 0.3) %>%
  map_dfr(function(ri_sens) {

@@

    # Re-run meta-analysis
    res_ri_sens <- update(res_brm, newdata = dat_ri_sens, refresh = 0)

    # Compute ICC
    var_experiment_ri_sens <- as.matrix(
      res_ri_sens,
      variable = "sd_article:experiment__Intercept"
    )^2
    var_article_ri_sens <- as.matrix(
      res_ri_sens,
      variable = "sd_article__Intercept"
    )^2
    var_total_ri_sens <- var_experiment_ri_sens + var_article_ri_sens
    icc_ri_sens <- var_article_ri_sens / var_total_ri_sens
    icc_row <- mean_qi(icc_ri_sens) %>%
      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)

    # Extract summary statistics as a data frame row
    with(summary(res_ri_sens), bind_rows(fixed, bind_rows(random))) %>%
      bind_rows(icc_row) %>%
      transmute(
        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
      ) %>%
      pivot_wider(names_from = parameter, values_from = Estimate) %>%
      bind_cols(`Assumed r_i` = print_num(ri_sens), .)
  }) -> tab_ri_sens

# Save the table
write_csv(tab_ri_sens, file = here(tables_dir, "ri_sens.csv"))
```

```{r, prior_sens}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```

>>>>

# Re-run the meta-analysis for different values of r_assumed
seq(-0.9, 0.9, by = 0.3) %>%
  set_names(., str_c("r = ", print_num(.))) %>%
  map(function(ri_sens) {

@@

    # Re-run meta-analysis
    update(res_brm, newdata = dat_ri_sens, refresh = 0)
  }) -> res_ri_sens

# Prior sensitivity analysis
list(
  "Intercept U(-10,10)" = c(
    set_prior("uniform(-10, 10)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "Intercept N(0,0.2)" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "SD U(0,10)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd")
  ),
  "SD Student-t(10,0,0.2)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  # Re-run the meta-analysis with different priors
  map(
    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
  ) -> res_prior_sens

# Create a table summarizing all sensitivity analyses
map2_dfr(
  c(res_ri_sens, res_prior_sens),
  c(names(res_ri_sens), names(res_prior_sens)),
  function(res, name) {

    # Compute ICC
    var_experiment <- as.matrix(
      res,
      variable = "sd_article:experiment__Intercept"
    )^2
    var_article <- as.matrix(
      res,
      variable = "sd_article__Intercept"
    )^2
    var_total <- var_experiment + var_article
    icc <- var_article / var_total
    icc_row <- mean_qi(icc) %>%
      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)

    # Create a data frame row of summary statistics
    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
      bind_rows(icc_row) %>%
      transmute(
        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
      ) %>%
      pivot_wider(names_from = parameter, values_from = Estimate) %>%
      bind_cols(Simulation = name, .)
  }
) -> tab_sens

# Save the table
write_csv(tab_sens, file = here(tables_dir, "sensitivity_analysis.csv"))
```
